---
title: "Earthquakes off Fiji"
subtitle: "Location and Magnitude"
author: "Vanda Dias"
date: "2 July 2017"
runtime: shiny
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Website Application

An website app has been created to show the location and magnitude of earthquakes near the Fiji islands. It is based on a data set from the datasets R package, quakes, that gives the locations of 1000 earthquakes off Fiji, since 1964 and of magnitude higher than 4.0 (Richter scale).

This app allows the user to select a group of data points based on a range of magnitude, and provides its map and data table with the location and characteristics of the group of earthquakes selected.

https://vandasdias.shinyapps.io/EarthquakesoffFiji/


## Instructions

1. Select throughout the slider, the range of the earthquakes´ magnitude to be shown,

2. In the main panel there are other two tabs that show the map and the data table associated with the selection,

2.1. The map tab shows the location of the selected earthquakes and it pops up their characteristics as latitude, longitude, depth and magnitude,

2.2. The table tab shows all the characteristics of the earthquakes selection in a data table,

3. As you move the slider, the selected points change automatically.


## Map

```{r echo = FALSE}
library(shiny)
library(leaflet)
earthquakes <- datasets::quakes
earthquakes$popup <- paste("Richter magnitude ", earthquakes$mag, "<br>", "Depth", earthquakes$depth, " km")
sidebarLayout(
    sidebarPanel(
      h6("Earthquakes' magnitude selected:"),
      renderText({
        paste(input$slider[1], " to ", input$slider[2])
      }),
      h2("---"),
      sliderInput("slider", "Select range of values", 4.0, 6.4, value = c(4.5, 5.0), 
                  step = 0.1)
    ),
    mainPanel(
      renderLeaflet({
        minmag <- input$slider[1]
        maxmag <- input$slider[2]
        selection <- earthquakes[earthquakes$mag >= minmag & 
                  earthquakes$mag <= maxmag, ]
        selection %>%
        leaflet() %>%
        addTiles() %>%
        addMarkers(popup = earthquakes$popup, clusterOptions = markerClusterOptions())
      })
    ))
```


## Table

```{r echo = FALSE}
sidebarLayout(
    sidebarPanel(
      h6("Earthquakes' magnitude selected:"),
      renderText({
        paste(input$slider2[1], " to ", input$slider2[2])
      }),
      h2("---"),
      sliderInput("slider2", "Select range of values", 4.0, 6.4, value = c(4.5, 5.0), 
                  step = 0.1)
    ),
    mainPanel(
      renderTable({
        minmag2 <- input$slider2[1]
        maxmag2 <- input$slider2[2]
        head(earthquakes[earthquakes$mag >= minmag2 & earthquakes$mag <= maxmag2, -6],10)
      })
    ))
```

